\documentclass[12pt]{amsart}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TYPICAL PACKAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{amsmath,amssymb}
\usepackage[all]{xy}
\usepackage{fullpage,enumerate}
\usepackage{url}
\usepackage{color}

\title{MATH 2250, Fall 2013}
\author{Instructor: Daniel Krashen}

\begin{document}
\pagenumbering{Alph}
\maketitle


\thispagestyle{empty}
\noindent
\textsc{Basic Course Information}

\begin{itemize}
\item
Lectures: TuTh 11:00am-12:15pm, Poultry Sciences 238 \\
Recitation: W 10:10am-11:00am, Poultry Sciences 238
\item 
Office Hour: W 1:15pm-2:15pm
\item
Office Phone: 706-542-2555 
\item
Email: \url{dkrashen@math.uga.edu} 
\item
Textbook: \textit{University Calculus}, Hasse, Weir, Thomas (1st or
2nd editions)
\end{itemize}

\medskip

\noindent
\textsc{Online Resources}

\begin{itemize}
\item
Course Webpage:  
\url{http://courses.dkrashen.org/f2013/2250/} 
\end{itemize}

\medskip

\noindent
\textsc{Course Objectives/Topics}

\begin{enumerate}[\hspace{\parindent}  1. ]
\item
The concept of the derivative.
\item
Calculate the derivatives of algebraic, exponential, logarithmic and
trigonometric functions.
\item
Model and solve optimization problems (minimization and
maximization).
\item
Calculate approximate values of functions, sketch graphs.
\item
The concept of the definite integral.
\item
Antiderivates and the evaluation of integrals. Substitution. 
\item
The fundamental theorem of calculus.
\end{enumerate}

\medskip

\noindent
\textsc{Grading Policy}

\begin{itemize}
\item
3 Mid-semester exams worth 20\% each (Sep 5, Oct 3, Nov 7)
\item
Homework worth 15\% (lowest 2
scores are dropped), 
\item
Final exam worth 25\%.
\end{itemize}

\medskip

\noindent
\textsc{Academic Honesty}

As a University of Georgia student, you have agreed to abide by the
University’s academic 
honesty policy, “A Culture of Honesty,” and the Student Honor Code.  All
academic work 
must meet the standards described in “A Culture of Honesty” found at: 
www.uga.edu/honesty.  Lack of knowledge of the academic honesty policy is
not a 
reasonable explanation for a violation.  Questions related to course
assignments and the 
academic honesty policy should be directed to the instructor.



\smallskip

\textit{The course syllabus is a general plan for the course; deviations
announced to the class by 
the instructor may be necessary.}


\end{document}

